Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/related_work.tex
expanded the souces already in smartphones related work section

\subsection{Learning from Smartphones}
Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.

>>>>

\subsection{Smartphones}
Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones. Research shows that perceptions of risk change as computing systems change. Chin et. al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, and find that these attitudes differ significantly ~\cite{chin2012measuring}. How people use these devices had also changed. Palen et. al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use cite\{palen2000going}. People also perceive and behave without a realistic understanding of the risks they are taking. Felt et. al\ examine the Android permission system and find that 17\% of participants paid attention to permissions, and only 3\% comprehended what these permissions meant.
